Make any stupid plot you want

### 2020-11-11 draft/sections/math.tex
math?

We propose that the mapping of a precise subset of data to a visual idiom ($I$) can be encapsulated in a class of functors called artists.

\begin{equation}
    A: \Gamma(V) \mapsto f:\T \mapsto R^{7}
\end{equation}
diagram here: gamma is a dataframe, t is like xkcd line (clear abstract), R7 is nice pixelated version 
\begin{definition}
    \item[$F$] fiber, which is the space of all possible values encoded in the fiber bundle
    \item[$K$] base space, tells how the values in the fibers are connected, is analogous to the indexer in data containers.
    \item[$V$] $F$ = $K \X F$ total space of the fiber bundle, which is space of all possible values on the index 
    \item[$\sigma$]
    \item[$\Gamma$]
    \item[$f$] analogous to spec (such as svg or raster) that render will rely on to translate image to screen
    \item[$\T \in CW$] cw simplex representing topology of visual elements on screen (embedded in code rather than explicit) 
    \item[$R^{7}$]  {R,G,B,A, x, y, z} pixel in display space
\end{definition}

\subsection{data}
We use fiberbundles as our underlying data representation because it concisely encodes topology\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989} and type \cite{spivakSIMPLICIALDATABASES}. 
For example, the iris dataset \cite{UCIMachineLearning} has a topology of disconnected points (k=0) and variables of type nominal (species type), and ratio (sepal and petal length and width). To encode this in a formal way, we rely on Butler's

Types and topology are (statement is line of equation)

\subsubsection{Data}
\begin{equation}
\Gamma(V) = 
\end{equation}

>>>>

We propose that the mapping of a precise subset of data to a visual idiom ($I$) can be encapsulated in a class of functors called artists.
Gluing keys along a base space

| Fiber Bundle | Spivak |
|--------------|--------|
| B | K |
| F | U |
| embedded in F  | (C, \sigma), \pi |
| E/V |  |
|   | \tau:  K-\Gamma(sigma) |
|   |

\begin{equation}
    A: {\sigma \in \Gamma(V)}\mapsto f:\T \mapsto R^{7}
\end{equation}
diagram here: gamma is a dataframe, t is like xkcd line (clear abstract), R7 is nice pixelated version 
\begin{definition}
    \item[$F$] fiber, which is the space of all possible values encoded in the fiber bundle
    \item[$K$] base space, tells how the values in the fibers are connected, is analogous to the indexer in data containers
    \item[$V$] $F$ = $K \X F$ total space of the fiber bundle, which is space of all possible values on the index 
    \item[$\sigma(k)$] section of the fiber at a single k, (record on the  r) (dataframe)
    \item[$\Gamma(V)$] set of all possible sections (Spivak - $\Gamma(\sigma))$ - is space of all dataframes (we use this in artists to generalize- class of functions/sigmas that the artist can work on)
    \item[$f$] analogous to spec (such as svg or raster) that render will rely on to translate image to screen
    \item[$\T \in CW$] cw simplex representing topology of visual elements on screen (embedded in code rather than explicit) 
    \item[$R^{7}$]  {R,G,B,A, x, y, z} pixel in display space
\end{definition}

\begin{equation}
    A: {\sigma \in \Gamma(V)}\mapsto f:\T \mapsto R^{7}
\end{equation}

\subsubsection{Data}
We use Butler's visualization model built on the mathematics of fiber bundles \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989} and Spivak's schema like description of fibers \cite{spivakSIMPLICIALDATABASES} as the basis of our data model.  The components of the fiber bundle are:
\begin{definition}
    \item[$K$] base space that describes the topology of the data, is the indexer in data contain
\end{definition}

\begin{center}
    \begin{tabular}{ c c c }
     term & mathematical definition & data container analogue\\
      $K$ & base space along which the data lies & indexer \\
      $F$ & fiber space from which possible values are pulled & schema \\
      $E$ & trivial: $F= K \times F$, non-trivial \dots &

    \end{tabular}
\end{center}

\begin{equation}

\end{equation}
